### 2015-02-07 cav-2015-tex/bisimulation.tex
Ran spell check.

The bisimulation proof in this section establishes the soundness and
completeness of the symbolic heap approach with respect to Generalized
Symbolic Execution (GSE). Intuitively, any properties proven with GSE
can also be proved using the symbolic heap algorithm.  GSE concretizes
the possible heap configurations along with various aliasing
relationships when an uninitialized field is dereferenced. The rules
for initializing and updating the fields in the Javalite semantics for
GSE are shown in the~\appref{app:gse}.

The proof shows the existence of a
bisimulation between sets of states related by GSE ($p \rgse
p^\prime$) and states related by the symbolic heap and update rules in this paper ($q \rsym
q^\prime$). The relations are on the universe of \emph{well-formed}
states $S$, which have the properties in \secref{sec:sh} with the
constraint that the states are \emph{feasible}: successors exist
unless at \cfgt{end}. Let $p \rgse p^\prime$ be a union over relations
for GSE (see appendix): $\rgse = \rgse^\mathit{A} \cup
\rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup
\rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup
\rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access
after evaluating the expression for the base reference $\lp
\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$, \emph{W} is
a field write after evaluating the expression for the right operand
$\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
in the operation or a false outcome, and \emph{\com} is everything
else in the language. Any state relation, say $\rightarrow_x$, is
trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The relation captures the notion of splitting groups of heaps at
certain operations. For example, suppose we have a set $P$ containing a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors in GSE: a non-null reference and a null reference. 
Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.

>>>>

The bisimulation proof in this section establishes the soundness and
completeness of the symbolic heap approach with respect to Generalized
Symbolic Execution (\gsetxt{}). Intuitively, any properties proven with~\gsetxt{}
can also be proved using the symbolic heap algorithm.~\gsetxt{} concretizes
the possible heap configurations along with various aliasing
relationships when an uninitialized field is dereferenced. The rules
for initializing and updating the fields in the Javalite semantics for
\gsetxt{} are shown in the~\appref{app:gse}.

The proof shows the existence of a
bisimulation between sets of states related by~\gsetxt{} ($p \rgse
p^\prime$) and states related by the symbolic heap and update rules in this paper ($q \rsym
q^\prime$). The relations are on the universe of \emph{well-formed}
states $S$, which have the properties in \secref{sec:sh} with the
constraint that the states are \emph{feasible}: successors exist
unless at \cfgt{end}. Let $p \rgse p^\prime$ be a union over relations
for~\gsetxt{} (see appendix): $\rgse = \rgse^\mathit{A} \cup
\rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup
\rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup
\rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access
after evaluating the expression for the base reference $\lp
\cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp$, \emph{W} is
a field write after evaluating the expression for the right operand
$\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
in the operation or a false outcome, and \emph{\com} is everything
else in the language. Any state relation, say $\rightarrow_x$, is
trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The relation captures the notion of splitting groups of heaps at
certain operations. For example, suppose we have a set $P$ containing a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors in~\gsetxt{}: a non-null reference and a null reference. 
Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.

### 2015-02-07 cav-2015-tex/evaluation.tex
Ran spell check.

    \hline
  \end{tabular}}
  \caption{Comparing the efficiency of the summary heap with the GSE and Lazier\# algorithms.}
  \label{tab:results}
\end{table*}
%\end{figure*}

%\subsection{Analysis}
We empirically evaluate the \symtxt{}
algorithm for analyzing programs with unbounded heap allocated
data in the context of symbolic execution.
To perform our evaluation we implemented a prototype of the \symtxt{} 
algorithm in Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} 
and evaluate its efficacy on three Java data structure artifacts.
SPF includes an implementation of GSE with lazy initialization.
In recent work, we implemented the  Lazier and Lazier\#
algorithms in SPF~\cite{Hillery:2014}.

@@

The path counts shown in Table~\ref{tab:results} also show the advantage
of the \symtxt{} algorithm over the \gsetxt{} and L\# algorithms, each of
which performs case-splitting during the analysis.
The number of paths explored by the \symtxt{} algorithm is strictly 
less than or equal to the number
of paths explored by \gsetxt{} for all artifacts. As a result,
fewer test cases will be generated to achieve the same control-flow 
path coverage when compared to GSE and Lazier\#.

>>>>

    \hline
  \end{tabular}}
  \caption{Comparing the efficiency of the summary heap with the~\gsetxt{} and Lazier\# algorithms.}
  \label{tab:results}
\end{table*}
%\end{figure*}

%\subsection{Analysis}
We empirically evaluate the \symtxt{}
algorithm for analyzing programs with unbounded heap allocated
data in the context of symbolic execution.
To perform our evaluation we implemented a prototype of the \symtxt{} 
algorithm in Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} 
and evaluate its efficacy on three Java data structure artifacts.
SPF includes an implementation of~\gsetxt{} with lazy initialization.
In recent work, we implemented the  Lazier and Lazier\#
algorithms in SPF~\cite{Hillery:2014}.

@@

The path counts shown in Table~\ref{tab:results} also show the advantage
of the \symtxt{} algorithm over the \gsetxt{} and L\# algorithms, each of
which performs case-splitting during the analysis.
The number of paths explored by the \symtxt{} algorithm is strictly 
less than or equal to the number
of paths explored by \gsetxt{} for all artifacts. As a result,
fewer test cases will be generated to achieve the same control-flow 
path coverage when compared to~\gsetxt{} and Lazier\#.

### 2015-02-07 cav-2015-tex/rw.tex
Ran spell check.

Initial work on symbolic execution largely focused on checking
properties of imperative programs with primitive
types~\cite{Clarke:76,King:76}.
% Limitations of early symbolic execution techniques included non-primitive data types, path explosion and non-symbolic operations. Subsequent adaptations have sought to overcome these limitations.
Several projects have generalized the core idea of symbolic execution,
enabling it to be applied to programs with more general types,
including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
generalized symbolic execution (GSE) techniques work by branching over
multiple copies of the system state during dereferencing operations,
exacerbating path explosion
% and fragmenting the path condition. Producing a complete path
%condition for a single given control flow path would require merging
%an exponential number of states.
Our work leverages the core idea in generalized symbolic
execution with lazy initialization using on-the-fly reasoning to model
a black-box input heap during symbolic execution, but avoids the
nondeterminism introduced by GSE by constructing a single summary heap
and polynomially-sized path condition for each control flow path.

@@

A number of dynamic symbolic execution (DSE) techniques either use
concretization when reasoning about references or require solvers that
support theories of
arrays~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. Sometimes,
however, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{}
underapproximates the possible heaps configurations when it
concretizes symbolic values. The SAGE~\dsetxt{}
engine~\cite{Elkarablieh:2009} includes more sophisticated methods for
reasoning about references, and can successfully reason about more
complicated examples. However, the heap model in SAGE prohibits
input-dependent memory allocation. The fixed-memory requirement means
that analyses of programs accepting indefinite input heaps may
terminate prematurely, even for the class of self-limiting
solver-compatible programs.

@@

%What I think: This paper is about how to handle pointers during dynamic symbolic execution. It handles pointer dereferences much like GSE, by resolving possible aliases at the time of the dereferencing, but does not seem to include the possibility of a “new” choice. One difference is that this method is adapted to allow pointer arithmetic. The memory model is basically a flat address space, without any explicit notion of a heap.

@@

%representation would work for GSE and heap summarization. Such a

>>>>

Initial work on symbolic execution largely focused on checking
properties of imperative programs with primitive
types~\cite{Clarke:76,King:76}.
% Limitations of early symbolic execution techniques included non-primitive data types, path explosion and non-symbolic operations. Subsequent adaptations have sought to overcome these limitations.
Several projects have generalized the core idea of symbolic execution,
enabling it to be applied to programs with more general types,
including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
generalized symbolic execution (\gsetxt{}) techniques work by branching over
multiple copies of the system state during dereferencing operations,
exacerbating path explosion.
% and fragmenting the path condition. Producing a complete path
%condition for a single given control flow path would require merging
%an exponential number of states.
Our work leverages the core idea in generalized symbolic
execution with lazy initialization using on-the-fly reasoning to model
a black-box input heap during symbolic execution, but avoids the
nondeterminism introduced by~\gsetxt{} by constructing a single summary heap
and polynomially-sized path condition for each control flow path.

@@

A number of dynamic symbolic execution (\dsetxt{}) techniques either use
concretization when reasoning about references or require solvers that
support theories of
arrays~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. Sometimes,
however, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{}
under-approximates the possible heaps configurations when it
concretizes symbolic values. The SAGE~\dsetxt{}
engine~\cite{Elkarablieh:2009} includes more sophisticated methods for
reasoning about references, and can successfully reason about more
complicated examples. However, the heap model in SAGE prohibits
input-dependent memory allocation. The fixed-memory requirement means
that analyses of programs accepting indefinite input heaps may
terminate prematurely, even for the class of self-limiting
solver-compatible programs.

@@

%What I think: This paper is about how to handle pointers during dynamic symbolic execution. It handles pointer dereferences much like~\gsetxt{}, by resolving possible aliases at the time of the dereferencing, but does not seem to include the possibility of a “new” choice. One difference is that this method is adapted to allow pointer arithmetic. The memory model is basically a flat address space, without any explicit notion of a heap.

@@

%representation would work for~\gsetxt{} and heap summarization. Such a
